ISYE 6740 HW 1

### 2024-08-28 msiddiqui60_HW1_report.tex
Adding the updated k-means code

>>>>

Third image source: https://commons.wikimedia.org/wiki/File:Greycat.jpg

Steps:
- convert images into pixel color representations
- define the number of clusters
- set the initial position of each cluster randomly (you are going to run this multiple times)
- use the l2-norm squared distance formula for each pixel to assign a cluster
- update the clusters
- repeat assignment until convergence (maybe set a condition until it stops)
